Think deep for reef resilience

### 2025-08-07 paper/paper_draft.qmd
Marking a paragraph to be revisited for clarity

Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater
thermal tolerance than reefs in lower coral cover clusters. This is in contrast with
literature suggesting corals have the capacity to adapt to increasing climate change
pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
[-@bairos-novak2021] that revealed high heritability of bleaching and survival response
traits, used to inform thermal tolerance trait distributions in this investigation. The lack
of influence of thermal tolerance on reef outcomes is likely due to reefs being impacted by
high levels of thermal stress early in timeseries and being unable to build thermal
tolerance to DHW levels greater than 9°C-weeks.

>>>>

Our findings do not suggest that reefs in ‘high’ cover clusters have greater thermal
tolerance than reefs in lower coral cover clusters. This is in contrast with literature
suggesting corals have the capacity to adapt to increasing climate change pressures
[@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
[-@bairos-novak2021] that revealed high heritability of bleaching and survival response
traits, used to inform thermal tolerance trait distributions in this investigation. The lack
of influence of thermal tolerance on reef outcomes is likely due to reefs being impacted by
high levels of thermal stress early in projected conditions and being unable to build
thermal tolerance to DHW levels greater than 9°C-weeks. **\[TI note: This paragraph needs to
be revisited\]**
